Thermodynamic fragments for magic states in quantum computation

### 2021-02-24 magic_paper.tex
A bit stuck. Not sure how to edit stuff

Even though non-stabilizerness is a necessary resource for universality, it has been proven insufficient for magic state distillation~\cite{cit:bravyi, cit:campbell}.
In fact, all states with non-negative Wigner distributions have been proven to be efficiently classically simulable in~\cite{cit:mari}, a result that serves as a generalization of the Gottesman-Knill theorem.
The Wigner distribution of a state in odd prime dimensions is discussed rigorously in~\cref{sec:wigner} and arises as the unique quasi-probability representation of quantum theory that identifies non-contextuality exactly with the states that are efficiently classically simulable~\cite{cit:howard2, cit:veitch2}.
In this framework, the stabilizer states are the only pure states represented with non-negative distributions~\cite{cit:gross3}. 
However, there exist mixed states with non-negative Wigner distributions that are not mixtures of stabilizer states~\cite{cit:gross}.
Therefore, stabilizer-preserving theories have been extended to a theory that preserves state ``Wigner positivity''~\cite{cit:wang}, formally defined in~\cref{sec:wigner} for odd prime dimensions.
Informally, it can be considered as the maximal theory of magic $\Rmax = (\Fmax, \Omax)$, where free states have non-negative Wigner distributions and free operations completely preserve this property.

@@

The generalised Pauli matrices $X, Z$ can be defined by their respective roles as shift and phase operators,
\begin{align}
    X \ket{k} &= \ket{k + 1} \label{eq:xpauli}\\
	Z \ket{k} &= \omega^k \ket{k}, \label{eq:zpauli}
\end{align}
where $\omega \coloneqq e^{2\pi i/d}$ is the $d$-th root of unity and addition is modulo $d$. The Hilbert space $\hd$ is associated with a phase space $\cal{P}_d \coloneqq \mathbb{Z}_d \times \mathbb{Z}_d$, where every point $\bmx \coloneqq (x, p)$ corresponds to a displacement operator, defined as
\begin{equation}\label{eq:ddef}
    D_{\bmx} \coloneqq \tau^{x p} X^{x} Z^{p},\ (x, p) \in \cal{P}_d.
\end{equation}
The phase factor $\tau \coloneqq -\omega^{1/2}$ ensures unitarity.
For a composite system with Hilbert space, $\hd = \hd[d_1] \otimes \dots \otimes \hd[d_n]$, the displacement operators are defined as
\begin{equation}\label{eq:composited}
    D_{\bmx} \coloneqq D_{(x_1, p_1)} \otimes \dots \otimes D_{(x_n, p_n)},
\end{equation}
where 
\begin{align}
	\bmx \coloneqq (x_1, x_2, \dots, x_n, p_1, \dots, p_n) \in \cal{P}_{d_1} \times \dots \times \cal{P}_{d_n},
\end{align}
denotes the phase space point for an $n$--copy system.

@@

We define the phase-point operators at every phase space point $\bmx \in \cal{P}_d$,
\begin{align}
	A_{\bmx} \coloneqq \frac{1}{d} \sum_{\bmz \in \cal{P}_d} \omega^{\eta(\bmx, \bmz)} D_{\bmz}, \label{eq:ax}
\end{align}
where $\eta(\bmx, \bmz)$ is the standard symplectic form, given explicitly by
\begin{equation}
	\eta(\bmx, \bmz) \coloneqq \bmz^T \begin{pmatrix}
		0  & \I \\ %\mathbbm{O}_n  & \id_n \\
		-\I & 0 \\ %-\id_n & \mathbbm{O}_n \\
	\end{pmatrix} \bmx.
\end{equation}

@@

For any quantum state $\rho$, the Wigner distribution $W_\rho(\bmx)$ is readily seen to be a $d^2$-dimensional quasi-probability distribution over $\cal{P}_d$ (see~\cref{app:wigner} for details).  In~\cref{fig:wstate_examples}, we show Wigner distributions of different types of qutrit states.
\begin{figure}%
    \centering
    \subfigure[][]{%
    \label{fig:maxmix}%
    \includegraphics[height=2cm]{figs/maxmixed.pdf}
    %\caption{Maximally mixed state $\frac{1}{3}\id$}%
    }\hspace{8pt}%
    \subfigure[][]{%
    \label{fig:zero}%
    \includegraphics[height=2cm]{figs/zerostate.pdf}
    %\caption{Zero state $\ketbra{0}{0}$}%
    }\\
    \subfigure[][]{%
    \label{fig:bound}%
    \includegraphics[height=2cm]{figs/boundstate.pdf}
    %\caption{Bound state}%
    }\hspace{8pt}%
    \subfigure[][]{%
    \label{fig:strange}%
    \includegraphics[height=2cm]{figs/strangestate.pdf}
    %\caption{Strange state $\ketbra{S}{S}$}%
    }
    \caption{\textbf{Qutrit Wigner distributions of varying magic.} 
    \subref{fig:maxmix} Maximally mixed state $\frac{1}{3}\id$; \subref{fig:zero} Stabilizer zero state $\ketbra{0}{0}$; \subref{fig:bound} A non-stabilizer Wigner-positive state; \subref{fig:strange} Magic strange state $\ket{{\rm{S}}} = \frac{1}{\sqrt{2}}(\ket{1} - \ket{2})$ \nick{CITE}.
    }%
    \label{fig:wstate_examples}
\end{figure}

@@

The single-qudit Hadamard gate $H$ and phase gate $S$ generate the $d$-dimensional Clifford group $\cal{C}_d$. \nick{CITE}
Their Wigner distributions are given by permutation matrices,
\begin{align}
    H &\coloneqq \frac{1}{\sqrt{d}}\sum_{j,k} \omega^{jk} \ketbra{j}{k}, \W[\bmy|\bmx]{H} = \delta_{y_0, -x_1}\delta_{y_1, x_0};\label{eq:H}\\
    S &\coloneqq \sum_k \tau^{k(k+1)} \ketbra{k}{k}, \W[\bmy|\bmx]{S} = \delta_{y_0, x_0}\delta_{y_1, x_0 + x_1 + 2^{-1}}.\label{eq:S}
\end{align}

@@

Equipped with the definitions of the Wigner distribution in odd prime dimensions, we can formally recast the maximal magic theory $\Rmax$ into a stochasticity setting.
The free states correspond to proper probability distributions 
\begin{equation}
    \Fmax \coloneqq \{ \rho: \W[\bmz]{\rho} \geq 0 \text{ for all } \bmz \in \cal{P}_d\}
\end{equation}

@@

Any magic theory $\R = (\F, \O)$ that has been proposed is a subtheory of $\Rmax$ in the sense that $\F \subseteq \Fmax$ and $\O \subseteq \Omax$, and as such it falls under this new stochasticity setting. 
For technical simplicity in what follows we assume that $\F$ is a closed set, and note that $\F_{\rm{ max}}$ is itself a closed set, since it is specified by a finite set of linear constraints of the form $\tr[ L\rho] \geq 0$ with operators $L \in \cal{B}(\cal{H})$ ensuring that the state is positive and Wigner-positive.

@@

In any magic theory, we can pick a certain free state, for example a stabilizer and view it as the analog of some thermal state $\gamma_\beta$.
Without loss of generality we can always write $\sigma = \frac{1}{\Z} e^{-\beta H}$ for some $\beta \ge 0$ and Hamiltonian $H$ (either effective or actual)\footnote{Technicalities arise for the case where $\sigma$ is not full rank, but this can be still described via $ \beta \rightarrow 0$ limiting process.}.
It then defines a set of free operations $\O_\sigma$ analogous to the thermal operations that preserve $\gamma_\beta$ the pre-order $\prec_{\R_\sigma}$ between these operations follows the rules of $\bmd$-majorization.

@@

Any quantum circuit aiming at a given magic state conversion $\rho \longrightarrow \tau$ possesses certain symmetries according to~\cref{thm:frag} that allow us to study the conversion within only certain $\sigma$-fragments.
As a simple example, the dephasing channel
\begin{equation}\label{eq:dephase}
	\Delta(\rho) = \sum_{k \in \mathbb{Z}_d} \ketbra{k}{k}\rho\ketbra{k}{k}
\end{equation}
removes coherent phases in the computational basis and therefore leaves exactly all mixtures of computational basis states invariant.
A model circuit consisting only of such dephasing channels can be fully analysed in the $\sigma$--fragments for the pure computational basis states $\sigma$ \nick{as seen in a theorem in the appendix}.

@@

\section{Magic in unital and thermal fragments}\label{sec:unital}
The unital fragment encompasses the circuits which preserve the maximally mixed state ($\id/d$) and so it includes many important families of circuits.

@@

Given this context, we can now state the following result, which is dependent on the free energy $F_\beta$ of a Gibbs state $\sigma$ where $ \beta F_\beta =  \beta\tr[H \sigma] - S(\sigma)$. We also fix the noisy Strange state to be of the form 
\begin{equation}
	\rho_{\rm{S}}(\epsilon) \coloneqq (1-\epsilon)\ketbra{\rm{S}} + \epsilon \frac{1}{3}\id,
\end{equation}
but more general states can be handled in exactly the same manner. In the following result we consider the bounds on distilling out pure states $|S\>\<S|$, with $\epsilon'=0$, but these bounds are easily generalised to purification bounds with $\epsilon' \ne 0$. Finally, we assume that $\epsilon \le 3/7$, so that the noisy magic state has non-zero negativity.
\begin{theorem}Let $\sigma$ be a qutrit stabilizer state, given by $\sigma = \frac{1}{\Z} e^{-\beta H}$ with $H$ having eigenvalues $E_0 \le E_1 \le E_2$, and where $\beta$ is an (effective) inverse temperature for the state. 
We define
\begin{equation}
	\beta_\star \coloneqq \frac{1}{E_2 - E_0} \ln{2}
\end{equation}
and for $\beta \leq \beta_\star$ define
\begin{equation}
	\epsilon_{\star}(\beta) \coloneqq 3 - \dfrac{18}{8-e^{(E_2 - E_0)\beta}}.
\end{equation}
a threshold error rate. Then any distillation rate $R(\epsilon, \beta)$ in the $\sigma$-fragment of a magic theory is bounded as follows:

If $\beta \leq \beta_{\star}$ and $\epsilon  \leq \epsilon_{\star}$,
\begin{equation}
	R(\epsilon,\beta) \leq 1 + \frac{\ln{\left( 1 - \frac{4}{3}\epsilon \right)}}{\beta (E_0 - F_\beta)}.
\end{equation}
If $\beta \leq \beta_{\star}$ and $\epsilon_{\star} < \epsilon$ then
\begin{equation}
	R(\epsilon, \beta) \le 1 + \frac{\ln{\left(1-\frac{1}{3}\epsilon \right)} - (E_2 - E_0)(\beta_{\star} - \beta)}{\beta (E_0 - F_\beta)},
\end{equation}
Otherwise if $\beta > \beta_{\star}$
\begin{equation}
	R(\epsilon, \beta) \leq  1+ \frac{\ln{\left(1-\frac{1}{3}\epsilon \right)}}{-\ln{2} + \beta (E_2 - F_\beta)}.
\end{equation}
\end{theorem}
A few comments can be given on this result. Firstly, the specific numerical factors in $\epsilon_\star$ are a result of our choice of magic state. Secondly, these bounds can almost certainly be improved through a finer analysis of the Lorenz curve. The existing bounds follow by considering the dominant terms in the rescaled Wigner distribution and do not, for example, take into account the Lorenz curve's peak structure.  Finally, it is striking that we obtain a Landauer-like condition with a characteristic temperature $kT_\star \ln 2 = E_2 - E_0$, where $kT_\star = \beta_\star^{-1}$. It is unclear whether this points to a generic feature that can be directly related to fundamental thermodynamic relations, such as the erasure cost of a single bit being $kT \ln 2$. Given that we work with qutrits this seems surprising, but does deserve further study.

\begin{figure}[t!]
    \centering
    \includegraphics[scale=0.5]{figs/rate_contour.png}
    \caption{\textbf{Bounds on magic distillation rates $R(\beta, \epsilon)$ within stabilizer fragments.}
    The vertical dashed line is the `Landauer-like' temperature threshold $\beta_\star$ and the diagonal dashed curve corresponds to the noise threshold $\epsilon_\star (\beta)$ at every $\beta \leq \beta_\star$. The unital fragment corresponds to the $\beta =0 $ line.
    }
    \label{fig:rate_contour}
\end{figure}

Consider a qutrit system with maximally Wigner-negative magic state $\ket{{\rm{S}}} = \frac{1}{\sqrt{2}}(\ket{1} - \ket{2})$.
It can be written in density operator form as
\begin{align}
	\ketbra{\rm{S}} = -\frac{1}{3} A_{\bmo} + \sum_{\bmx \neq \bmo} \frac{1}{6} A_{\bmx},
\end{align}
where $\bmx$ ranges in the $3$-dimensional phase space $\cal{P}_d[3]$.
This is the pure Strange state visualised in~\cref{fig:strange}.
We allow for isotropic (uniform) noise, so that the system state is a convex sum of the pure Strange state and the maximally mixed state,
\begin{equation}
	\rho_{\rm{S}}(\epsilon) \coloneqq (1-\epsilon)\ketbra{\rm{S}} + \epsilon \frac{1}{3}\id,
\end{equation}
where we choose to restrict the noise level, $0 \leq \epsilon \leq \frac{3}{7}$, so that the Wigner distribution of the state always contains a negative component which is greater than the remaining 8 positive components.

@@

In the previous section we introduced the notion of $\sigma$--fragments for any resource theory of magic. In this section we pause to generalise this concept to an arbitrary resource theory and explain precisely how it connects with resource monotones. The busy reader more focussed on magic may skip this section. \nick{restate}

State convertibility within a given resource theory is often a hard question to address due to the intricate structure of the theory.
In general, the structure of a theory $\R$ is described by a pre-order $\prec_\R$ and usually resource monotones are employed to reduce this structure into a simple real number ordering\nick{CITE}.
The subdivisions of magic theories into $\sigma$--fragments suggests a new approach towards investigating state convertibility which retains more structure of the origin theory than a measure can.

>>>>

Even though non-stabilizerness is a necessary resource for universality, it has been proven insufficient for magic state distillation~\cite{cit:bravyi, cit:campbell}.
In fact, all states with non-negative Wigner distributions have been proven to be efficiently classically simulable in~\cite{cit:mari}, a result that serves as a generalization of the Gottesman-Knill theorem.
The Wigner distribution of a state in odd prime dimensions is discussed rigorously in~\cref{sec:wigner} and arises as the unique quasi-probability representation of quantum theory that identifies non-contextuality exactly with the states that are efficiently classically simulable~\cite{cit:howard2, cit:veitch2}.
In this framework, the stabilizer states are the only pure states represented with non-negative distributions~\cite{cit:gross3}. 
However, there exist mixed states with non-negative Wigner distributions that are not mixtures of stabilizer states~\cite{cit:gross}.
Therefore, stabilizer-preserving theories have been extended to a theory that preserves state ``Wigner positivity''~\cite{cit:wang}, formally defined in~\cref{sec:wigner} for odd prime dimensions.
Informally, it can be considered as the maximal theory of magic $\Rmax = (\Fmax, \Omax)$, where free states have non-negative Wigner distributions and free operations completely preserve this property.\\

@@

The generalised Pauli matrices $X, Z$ can be defined by their respective roles as shift and phase operators,
\begin{align}
    X \ket{k} &= \ket{k + 1} \label{eq:xpauli}\\
	Z \ket{k} &= \omega^k \ket{k}, \label{eq:zpauli}
\end{align}
where $\omega \coloneqq e^{2\pi i/d}$ is the $d$-th root of unity and addition is modulo $d$. The Hilbert space $\hd$ is associated with a phase space $\cal{P}_d \coloneqq \mathbb{Z}_d \times \mathbb{Z}_d$, where every point $\bmx \coloneqq (x, p)$ corresponds to a displacement operator, defined as
\begin{equation}\label{eq:ddef}
    D_{\bmx} \coloneqq \tau^{x p} X^{x} Z^{p},\ (x, p) \in \cal{P}_d.
\end{equation}
The phase factor $\tau \coloneqq -\omega^{1/2}$ ensures unitarity.
For a composite system with Hilbert space, $\hd = \hd[d_1] \otimes \dots \otimes \hd[d_n]$, the displacement operators are defined as
\begin{equation}\label{eq:composited}
    D_{\bmx} \coloneqq D_{(x_1, p_1)} \otimes \dots \otimes D_{(x_n, p_n)},
\end{equation}
where 
\begin{align*}
	\bmx \coloneqq (x_1, p_1, x_2, p_2, \dots, x_n, p_n) \in \cal{P}_{d_1} \times \dots \times \cal{P}_{d_n},
\end{align*}
denotes the phase space point for an $n$--copy system.

@@

We define the phase-point operators at every phase space point $\bmx \in \cal{P}_d$,
\begin{align}
	A_{\bmx} \coloneqq \frac{1}{d} \sum_{\bmz \in \cal{P}_d} \omega^{\eta(\bmx, \bmz)} D_{\bmz}, \label{eq:ax}
\end{align}
where $\eta(\bmx, \bmz)$ is the standard symplectic form, given explicitly by
\begin{equation}
	\eta(\bmx, \bmz) \coloneqq \bmz^T \begin{pmatrix}
		0  & \id \\ %\mathbbm{O}_n  & \id_n \\
		-\id & 0 \\ %-\id_n & \mathbbm{O}_n \\
	\end{pmatrix} \bmx.
\end{equation}

@@

For any quantum state $\rho$, the Wigner distribution $W_\rho(\bmx)$ is readily seen to be a $d^2$-dimensional quasi-probability distribution over $\cal{P}_d$ (see~\cref{app:wigner} for details).  In~\cref{fig:wstate_examples}, we show Wigner distributions of different types of qutrit states.
\begin{figure}%
    \centering
    \subfigure[][]{%
    \label{fig:maxmix}%
    \includegraphics[height=2cm]{figs/maxmixed.pdf}
    %\caption{Maximally mixed state $\frac{1}{3}\id$}%
    }\hspace{8pt}%
    \subfigure[][]{%
    \label{fig:zero}%
    \includegraphics[height=2cm]{figs/zerostate.pdf}
    %\caption{Zero state $\ketbra{0}{0}$}%
    }\\
    \subfigure[][]{%
    \label{fig:bound}%
    \includegraphics[height=2cm]{figs/boundstate.pdf}
    %\caption{Bound state}%
    }\hspace{8pt}%
    \subfigure[][]{%
    \label{fig:strange}%
    \includegraphics[height=2cm]{figs/strangestate.pdf}
    %\caption{Strange state $\ketbra{S}{S}$}%
    }
    \caption{\textbf{Qutrit Wigner distributions of varying magic.} 
    \subref{fig:maxmix} Maximally mixed state $\frac{1}{3}\id$; \subref{fig:zero} Stabilizer zero state $\ketbra{0}{0}$; \subref{fig:bound} A non-stabilizer Wigner-positive state; \subref{fig:strange} Magic Strange state $\ket{{\rm{S}}} = \frac{1}{\sqrt{2}}(\ket{1} - \ket{2})$, coined in~\cite{cit:veitch2}.
    }%
    \label{fig:wstate_examples}
\end{figure}

@@

The single-qudit Hadamard gate $H$ and phase gate $S$ generate the $d$-dimensional Clifford group $\cal{C}_d$~\cite{cit:gottesman1998}.
Their Wigner distributions are given by permutation matrices,
\begin{align}
    H &\coloneqq \frac{1}{\sqrt{d}}\sum_{j,k} \omega^{jk} \ketbra{j}{k}, \W[\bmy|\bmx]{H} = \delta_{y_0, -x_1}\delta_{y_1, x_0};\label{eq:H}\\
    S &\coloneqq \sum_k \tau^{k(k+1)} \ketbra{k}{k}, \W[\bmy|\bmx]{S} = \delta_{y_0, x_0}\delta_{y_1, x_0 + x_1 + 2^{-1}}.\label{eq:S}
\end{align}
\nick{Remove above paragraph?}

@@

Equipped with the definitions of the Wigner distribution in odd prime dimensions, we can formally recast the maximal magic theory $\Rmax$ into a stochasticity setting.
The free states correspond to proper probability distributions 
\begin{equation}
    \Fmax \coloneqq \{ \rho: \W[\bmx]{\rho} \geq 0 \text{ for all } \bmx \in \cal{P}_d\}
\end{equation}

@@

Every established magic theory $\R = (\F, \O)$ is a subtheory of $\Rmax$ in the sense that $\F \subseteq \Fmax$ and $\O \subseteq \Omax$, and as such it falls under this new stochasticity setting. 
For technical simplicity in what follows we assume that $\F$ is a closed set, and note that $\F_{\rm{ max}}$ is itself a closed set, since it is specified by a finite set of linear constraints of the form $\tr[ L\rho] \geq 0$ with operators $L \in \cal{B}(\cal{H})$ ensuring that the state is positive and Wigner-positive.

@@

In any magic theory, we can pick a certain free state, for example a stabilizer and view it as the analog of some thermal state $\gamma_\beta$.
Without loss of generality we can always write a state $\sigma$ as a thermal state, $\sigma = \gamma_\beta \coloneqq \frac{1}{\Z} e^{-\beta H}$ for some $\beta \ge 0$ and Hamiltonian $H$ (either effective or actual)\footnote{Technicalities arise for the case where $\sigma$ is not full rank, but this can be still described via $ \beta \rightarrow 0$ limiting process.}.
It then defines a set of free operations $\O_\sigma$ analogous to the thermal operations that preserve $\gamma_\beta$ the pre-order $\prec_{\R_\sigma}$ between these operations follows the rules of $\bmd$-majorization.

@@

Any quantum circuit aiming at a given magic state conversion $\rho \longrightarrow \tau$ possesses certain symmetries according to~\cref{thm:frag} that allow us to study the conversion within only certain $\sigma$-fragments.
As a simple example, the dephasing channel
\begin{equation}\label{eq:dephase}
	\Delta(\rho) = \sum_{k \in \mathbb{Z}_d} \ketbra{k}{k}\rho\ketbra{k}{k}
\end{equation}
removes coherent phases in the computational basis and therefore leaves exactly all mixtures of computational basis states invariant.
A model circuit consisting only of such dephasing channels can be fully analysed in the $\sigma$--fragments for the pure computational basis states $\sigma$.

@@

\section{Magic in the unital fragment}\label{sec:unital}
The unital fragment encompasses the circuits which preserve the maximally mixed state ($\id/d$) and so it includes many important families of circuits.

@@

Given this context, we can now state the following result, which is dependent on the free energy $F_\beta$ of a Gibbs state $\sigma$ where $ \beta F_\beta =  \beta\tr[H \sigma] - S(\sigma)$. We also fix the noisy Strange state to be of the form 
\begin{equation}
	\rho_{\rm{S}}(\epsilon) \coloneqq (1-\epsilon)\ketbra{\rm{S}} + \epsilon \frac{1}{3}\id,
\end{equation}
but more general states can be handled in exactly the same manner. In the following result we consider the bounds on distilling out pure states $|S\>\<S|$, with $\epsilon'=0$, but these bounds are easily generalised to purification bounds with $\epsilon' \ne 0$. Finally, we assume that $\epsilon \le 3/7$, so that the noisy magic state has \nick{a dominant negative component}.
\begin{theorem}Let $\sigma$ be a qutrit stabilizer state, given by $\sigma = \frac{1}{\Z} e^{-\beta H}$ with $H$ having eigenvalues $E_0 \le E_1 \le E_2$, and where $\beta$ is an (effective) inverse temperature for the state. 
We define
\begin{equation}
	\beta_\star \coloneqq \frac{1}{E_2 - E_0} \ln{2}
\end{equation}
and for $\beta \leq \beta_\star$ define
\begin{equation}
	\epsilon_{\star}(\beta) \coloneqq 3 - \dfrac{18}{8-e^{(E_2 - E_0)\beta}}.
\end{equation}
a threshold error rate. Then any distillation rate $R(\epsilon, \beta)$ in the $\sigma$-fragment of a magic theory is bounded as follows:

If $\beta \leq \beta_{\star}$ and $\epsilon  \leq \epsilon_{\star}$,
\begin{equation}
	R(\epsilon,\beta) \leq 1 + \frac{\ln{\left( 1 - \frac{4}{3}\epsilon \right)}}{\beta (E_0 - F_\beta)}.
\end{equation}
If $\beta \leq \beta_{\star}$ and $\epsilon_{\star} < \epsilon$, then
\begin{equation}
	R(\epsilon, \beta) \le 1 + \frac{\ln{\left(1-\frac{1}{3}\epsilon \right)} - (E_2 - E_0)(\beta_{\star} - \beta)}{\beta (E_0 - F_\beta)},
\end{equation}
Otherwise if $\beta > \beta_{\star}$,
\begin{equation}
	R(\epsilon, \beta) \leq  1+ \frac{\ln{\left(1-\frac{1}{3}\epsilon \right)}}{-\ln{2} + \beta (E_2 - F_\beta)}.
\end{equation}
\end{theorem}
A few comments can be given on this result. Firstly, the specific numerical factors in $\epsilon_\star$ are a result of our choice of magic state. Secondly, these bounds can almost certainly be improved through a finer analysis of the Lorenz curve. The existing bounds follow by considering the dominant terms in the rescaled Wigner distribution and do not, for example, take into account the Lorenz curve's peak structure.  Finally, it is striking that we obtain a Landauer-like condition with a characteristic temperature $kT_\star \ln 2 = E_2 - E_0$, where $kT_\star = \beta_\star^{-1}$. It is unclear whether this points to a generic feature that can be directly related to fundamental thermodynamic relations, such as the erasure cost of a single bit being $kT \ln 2$. Given that we work with qutrits this seems surprising, but does deserve further study.

\begin{figure}[t!]
    \centering
    \includegraphics[scale=0.5]{figs/rate_contour.png}
    \caption{\textbf{Bounds on magic distillation rates $R(\epsilon, \beta)$ within stabilizer fragments.}
    The vertical dashed line is the `Landauer-like' temperature threshold $\beta_\star$ and the diagonal dashed curve corresponds to the noise threshold $\epsilon_\star (\beta)$ at every $\beta \leq \beta_\star$. The unital fragment corresponds to the $\beta =0 $ line.
    }
    \label{fig:rate_contour}
\end{figure}

Consider a qutrit system with maximally Wigner-negative magic state $\ket{{\rm{S}}} = \frac{1}{\sqrt{2}}(\ket{1} - \ket{2})$.
It can be written in density operator form as
\begin{align}
	\ketbra{\rm{S}} = -\frac{1}{3} A_{\bmo} + \sum_{\bmx \neq \bmo} \frac{1}{6} A_{\bmx},
\end{align}
where $\bmx$ ranges in the $3$-dimensional phase space $\cal{P}_d$.
This is the pure Strange state visualised in~\cref{fig:strange}.
We allow for isotropic (uniform) noise, so that the system state is a convex sum of the pure Strange state and the maximally mixed state,
\begin{equation}
	\rho_{\rm{S}}(\epsilon) \coloneqq (1-\epsilon)\ketbra{\rm{S}} + \epsilon \frac{1}{3}\id,
\end{equation}
where we choose to restrict the noise level, $0 \leq \epsilon \leq \frac{3}{7}$, so that the Wigner distribution of the state always contains a negative component which is greater than the remaining 8 positive components.

@@

So far we have introduced the notion of $\sigma$--fragments for any resource theory of magic. 
In this section we pause to generalise this concept to an arbitrary resource theory and explain precisely how it connects with resource monotones. 
The busy reader more focussed on magic may skip this section.

State convertibility within a given resource theory is often a hard question to address due to the intricate structure of the theory.
In general, the structure of a theory $\R$ is described by a pre-order $\prec_\R$ and usually resource monotones are employed to reduce this structure into a simple real number ordering \nick{CITE}.
The subdivisions of magic theories into $\sigma$--fragments suggests a new approach towards investigating state convertibility which retains more structure of the originaltheory than a measure can.
